### 2019-08-31 publications.tex
Escape of radiation accepted.

\subsection{Refereed Publications}

\href{https://ui.adsabs.harvard.edu/search/filter_database_fq_database=OR&filter_database_fq_database=database\%3A\%22astronomy\%22&fq=\%7B!type\%3Daqp\%20v\%3D\%24fq_database\%7D&fq_database=(database\%3A\%22astronomy\%22)&q=\%3Dauthor\%3A(\%22Kim\%2C\%20Jeong-Gyu\%22)&sort=date\%20desc\%2C\%20bibcode\%20desc}{\color{dodgerblue}{(ADS
Link)}}

\begin{benumerate}{7}
\item \textit{Modeling UV Radiative Feedback from Massive Stars: II. Dispersal
of Star-Forming Giant Molecular Clouds by Photoionization and Radiation
Pressure} \\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, ApJ, 859,
68
\item \textit{Modeling UV Radiative Feedback from Massive Stars: I.
Implementation of Adaptive Ray Tracing Method and Tests}\\ \textbf{Kim, J.-G.},
Kim, W.-T., Ostriker, E. C.,\& Skinner A. M. 2017, ApJ, 851, 93
\item \textit{Disruption of Molecular Clouds by Expansion of Dusty H II
Regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2016, ApJ, 819,
137
\item \textit{Instability of Magnetized Ionization Fronts Surrounding H II
regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T. 2014, ApJ, 797, 135
\item \textit{Nature of Wiggle Instability of Galactic Spiral Shocks}\\ Kim,
W.-T., Kim, Y., \& \textbf{Kim, J.-G.} 2014, ApJ, 789, 68
\item \textit{Instability of Evaporation Fronts in the Interstellar Medium}\\
  \textbf{Kim, J.-G.}, Kim, W.-T. 2013, ApJ, 779, 48
\item \textit{Gravitational Instability of Rotating, Pressure-Confined,
    Polytropic Gas Disks with Vertical Stratification} \\ \textbf{Kim, J.-G.},
  Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012, ApJ, 761, 131
\end{benumerate}

\subsection{Papers in Preparation}
\begin{enumerate}
\item[] \textit{Modeling UV Radiative Feedback from Massive Stars: III. Escape
    of Radiation from Star-Forming Giant Molecular Clouds} \\ \textbf{Kim,
    J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, \textit{ApJ submitted}
\item[] \textit{Recovery of Cloud-Scale Star Formation Rate Based on Ionizing
    Luminosity: Calibration for Escape of Radiation} \\ \textbf{Kim, J.-G.} \&
  Ostriker, E. C. \textit{2019, in prep}
\item[] \textit{Diffuse Ionized Gas in TIGRESS Simulations of the ISM}\\ Kado
  Fong, E., \textbf{Kim, J.-G.}, Kim, C.-G., \& Ostriker, E. C. \textit{2019, in
    prep}
\end{enumerate}

>>>>

\subsection{Refereed Publications -- \href{https://ui.adsabs.harvard.edu/search/filter_database_fq_database=OR&filter_database_fq_database=database\%3A\%22astronomy\%22&fq=\%7B!type\%3Daqp\%20v\%3D\%24fq_database\%7D&fq_database=(database\%3A\%22astronomy\%22)&q=\%3Dauthor\%3A(\%22Kim\%2C\%20Jeong-Gyu\%22)&sort=date\%20desc\%2C\%20bibcode\%20desc}{\color{dodgerblue}{ADS
Search}}}

\begin{benumerate}{8}
\item \textit{Modeling UV Radiative Feedback from Massive Stars: III. Escape
    of Radiation from Star-Forming Giant Molecular Clouds} \\ \textbf{Kim,
    J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, \textit{ApJ accepted}
\item \textit{Modeling UV Radiative Feedback from Massive Stars: II. Dispersal
of Star-Forming Giant Molecular Clouds by Photoionization and Radiation
Pressure} \\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, ApJ, 859,
68
\item \textit{Modeling UV Radiative Feedback from Massive Stars: I.
Implementation of Adaptive Ray Tracing Method and Tests}\\ \textbf{Kim, J.-G.},
Kim, W.-T., Ostriker, E. C.,\& Skinner A. M. 2017, ApJ, 851, 93
\item \textit{Disruption of Molecular Clouds by Expansion of Dusty H II
Regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2016, ApJ, 819,
137
\item \textit{Instability of Magnetized Ionization Fronts Surrounding H II
regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T. 2014, ApJ, 797, 135
\item \textit{Nature of Wiggle Instability of Galactic Spiral Shocks}\\ Kim,
W.-T., Kim, Y., \& \textbf{Kim, J.-G.} 2014, ApJ, 789, 68
\item \textit{Instability of Evaporation Fronts in the Interstellar Medium}\\
  \textbf{Kim, J.-G.}, Kim, W.-T. 2013, ApJ, 779, 48
\item \textit{Gravitational Instability of Rotating, Pressure-Confined,
    Polytropic Gas Disks with Vertical Stratification} \\ \textbf{Kim, J.-G.},
  Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012, ApJ, 761, 131
\end{benumerate}

\subsection{Papers in Preparation}
\begin{enumerate}
\item[] \textit{Diffuse Ionized Gas in TIGRESS Simulations of the ISM}\\
  Kado-Fong, E., \textbf{Kim, J.-G.}, Kim, C.-G., \& Ostriker, E. C.
  \textit{2019, to be submitted}
\item[] \textit{Recovery of Cloud-Scale Star Formation Rate Based on Ionizing
    Luminosity: Calibration for Escape of Radiation} \\ \textbf{Kim, J.-G.} \&
  Ostriker, E. C. \textit{2019, in prep}
\item[] \textit{TIGRESS-RT: Implementation New Heating/Cooling Module with
    Adaptive Ray Tracing}\\ \textbf{Kim, J.-G.}, Gong, M., Kim, C.-G., \&
  Ostriker, E. C.
\end{enumerate}
